---
title: "Febreze (Mar-Jun)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.jpg

---

```{r setup, include=FALSE}
library(flexdashboard)
library(readxl)
library(ggplot2)
library(plotly)
library(knitr)
library(d3heatmap)
library(dplyr)

df = read_excel("base_heatmaps.xlsx", sheet = 4)

```


Historico {data-navmenu="Add to cart-Medio"}
=====================================


```{r, echo=FALSE}

can=df %>% group_by(Date, Source) %>% summarise(n=sum(Add_to_cart))


ca=ggplot(can, aes(x=Date,y=n, fill=Source)) + labs(x="Date",y="N?mero de add to cart",title="Add to cart Mar - Jun 2019")+
  geom_bar(stat="identity")+theme_minimal()


ggplotly(ca)

```



Mes {data-navmenu="Add to cart-Medio"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(Month,Source) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(Month)

mes= mes %>% group_by(Month)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=Month,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="Month",y="Total",title="Total Add to cart por medio")+
  scale_x_discrete(limit=c('Ene','Feb','Mar','Abr','May','Jun','Jul','Ago','Sep','Oct','Nov','Dic'))  

ggplotly(mess)


```



Dia {data-navmenu="Add to cart-Medio"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_compra,Source) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(dia_compra)

mes= mes %>% group_by(dia_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_compra,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a del mes",y="Total",title="Total Add to cart por medio")

ggplotly(mess)


```


Dia de la semana {data-navmenu="Add to cart-Medio"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_semana_compra,Source) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(dia_semana_compra)

mes= mes %>% group_by(dia_semana_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_semana_compra,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a de la semana",y="Total",title="Total Add to cart por medio")+
  scale_x_discrete(limit=c('lun','mar','mi?','jue','vie','s?b','dom'))  

ggplotly(mess)


```


Historico {data-navmenu="Add to cart-Ad_content"}
=====================================


```{r, echo=FALSE}

can=df %>% group_by(Date, Ad_content) %>% summarise(n=sum(Add_to_cart))


ca=ggplot(can, aes(x=Date,y=n, fill=Ad_content)) + labs(x="Date",y="N?mero de add to cart",title="Add to cart Mar - Jun 2019")+
  geom_bar(stat="identity")+theme_minimal()+theme(legend.position = 'none')


ggplotly(ca)

```


Mes {data-navmenu="Add to cart-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(Month,Ad_content) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(Month)

mes= mes %>% group_by(Month)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=Month,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="Month",y="Total",title="Total Add to cart por add content")+
  scale_x_discrete(limit=c('Ene','Feb','Mar','Abr','May','Jun','Jul','Ago','Sep','Oct','Nov','Dic'))  

ggplotly(mess)


```



Dia {data-navmenu="Add to cart-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_compra,Ad_content) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(dia_compra)

mes= mes %>% group_by(dia_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a del mes",y="Total",title="Total Add to cart por ad content")

ggplotly(mess)


```


Dia de la semana {data-navmenu="Add to cart-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_semana_compra,Ad_content) %>% 
  summarise(n=sum(Add_to_cart))  %>% arrange(dia_semana_compra)

mes= mes %>% group_by(dia_semana_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_semana_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a de la semana",y="Total",title="Total Add to cart por add content")+
  scale_x_discrete(limit=c('lun','mar','mi?','jue','vie','s?b','dom'))  

ggplotly(mess)


```



Historico {data-navmenu="Sesiones-Medio"}
=====================================


```{r, echo=FALSE}

can=df %>% group_by(Date, Source) %>% summarise(n=sum(Sesiones))


ca=ggplot(can, aes(x=Date,y=n, fill=Source)) + labs(x="Date",y="N?mero de sesiones",title="Sesiones Mar - Jun 2019")+
  geom_bar(stat="identity")+theme_minimal()


ggplotly(ca)

```


Mes {data-navmenu="Sesiones-Medio"}
=====================================


```{r, echo=FALSE}


mes=df %>% group_by(Month,Source) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(Month)

mes= mes %>% group_by(Month)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=Month,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="Month",y="Total",title="Sesiones por medio")+
  scale_x_discrete(limit=c('Ene','Feb','Mar','Abr','May','Jun','Jul','Ago','Sep','Oct','Nov','Dic'))  

ggplotly(mess)


```



Dia {data-navmenu="Sesiones-Medio"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_compra,Source) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(dia_compra)

mes= mes %>% group_by(dia_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_compra,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a del mes",y="Total",title="Sesiones por medio")

ggplotly(mess)


```


Dia de la semana {data-navmenu="Sesiones-Medio"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_semana_compra,Source) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(dia_semana_compra)

mes= mes %>% group_by(dia_semana_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_semana_compra,y=n,fill=Source,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a de la semana",y="Total",title="Sesiones por medio")+
  scale_x_discrete(limit=c('lun','mar','mi?','jue','vie','s?b','dom'))  

ggplotly(mess)


```


Historico {data-navmenu="Sesiones-Ad_content"}
=====================================


```{r, echo=FALSE}

can=df %>% group_by(Date, Ad_content) %>% summarise(n=sum(Sesiones))


ca=ggplot(can, aes(x=Date,y=n, fill=Ad_content)) + labs(x="Date",y="N?mero de sesiones",title="Sesiones Mar - Jun 2019")+
  geom_bar(stat="identity")+theme_minimal()+theme(legend.position = 'none')


ggplotly(ca)

```

Mes {data-navmenu="Sesiones-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(Month,Ad_content) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(Month)

mes= mes %>% group_by(Month)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=Month,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="Month",y="Total",title="Sesiones por add content")+
  scale_x_discrete(limit=c('Ene','Feb','Mar','Abr','May','Jun','Jul','Ago','Sep','Oct','Nov','Dic'))  

ggplotly(mess)


```



Dia {data-navmenu="Sesiones-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_compra,Ad_content) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(dia_compra)

mes= mes %>% group_by(dia_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a del mes",y="Total",title="Sesiones por ad content")

ggplotly(mess)


```


Dia de la semana {data-navmenu="Sesiones-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_semana_compra,Ad_content) %>% 
  summarise(n=sum(Sesiones))  %>% arrange(dia_semana_compra)

mes= mes %>% group_by(dia_semana_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_semana_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a de la semana",y="Total",title="Sesiones por add content")+
  scale_x_discrete(limit=c('lun','mar','mi?','jue','vie','s?b','dom'))  

ggplotly(mess)


```



Historico {data-navmenu="CR-Ad_content"}
=====================================

### CR(Add_to_cart/Sesiones) por Ad_content

```{r, echo=FALSE}

can=df %>% group_by(Date, Ad_content) %>% summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100)


ca=ggplot(can, aes(x=Date,y=n, fill=Ad_content)) + labs(x="Date",y="CR",title="CR por ad content Mar - Jun 2019")+
  geom_bar(stat="identity")+theme_minimal()+theme(legend.position = 'none')


ggplotly(ca)

```

Mes {data-navmenu="CR-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(Month,Ad_content) %>% summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100)  %>% arrange(Month)

mes= mes %>% group_by(Month)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=Month,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="Month",y="CR",title="CR por add content")+
  scale_x_discrete(limit=c('Ene','Feb','Mar','Abr','May','Jun','Jul','Ago','Sep','Oct','Nov','Dic'))  

ggplotly(mess)


```



Dia {data-navmenu="CR-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_compra,Ad_content) %>% summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100)  %>% arrange(dia_compra)

mes= mes %>% group_by(dia_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a del mes",y="CR",title="CR por ad content")

ggplotly(mess)


```


Dia de la semana {data-navmenu="CR-Ad_content"}
=====================================


```{r, echo=FALSE}



mes=df %>% group_by(dia_semana_compra,Ad_content) %>% summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100)  %>% arrange(dia_semana_compra)

mes= mes %>% group_by(dia_semana_compra)%>%   mutate(Participacion=round((n/sum(n))*100,2))


mess=ggplot(mes,aes(x=dia_semana_compra,y=n,fill=Ad_content,label = paste0(Participacion, "%")))+
  geom_bar(stat="identity")+
  theme_minimal()+
  labs(x="D?a de la semana",y="CR",title="CR por add content")+
  scale_x_discrete(limit=c('lun','mar','mi?','jue','vie','s?b','dom'))  

ggplotly(mess)


```







Add to cart {data-navmenu="Heatmaps"}
=====================================
  
  
### Add to cart
  
```{r, echo=FALSE}


dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>% summarise(n=sum(Add_to_cart)) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```





Sesiones {data-navmenu="Heatmaps"}
=====================================
  
  
### Sesiones
  
```{r, echo=FALSE}


dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>% summarise(n=sum(Sesiones)) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```



CR {data-navmenu="Heatmaps"}
=====================================
  
  
### CR (Add to cart/sesiones)
  
```{r, echo=FALSE}


dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>% summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```



Facebook {data-navmenu="Add to cart-Medio"}
====================================================


### Facebook
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='facebook') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Google {data-navmenu="Add to cart-Medio"}
====================================================


### Google
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='google') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Mediamath {data-navmenu="Add to cart-Medio"}
====================================================


### Mediamath
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='mediamath') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Peoplemedia {data-navmenu="Add to cart-Medio"}
====================================================


### Peoplemedia
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='peoplemedia') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Teads {data-navmenu="Add to cart-Medio"}
====================================================


### Teads
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='teads') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```



Youtube {data-navmenu="Add to cart-Medio"}
====================================================


### Youtube
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='youtube') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = add)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Add to cart, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```





Facebook {data-navmenu="Sesiones-Medio"}
====================================================


### Facebook
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='facebook') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Google {data-navmenu="Sesiones-Medio"}
====================================================


### Google
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='google') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Mediamath {data-navmenu="Sesiones-Medio"}
====================================================


### Mediamath
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='mediamath') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Peoplemedia {data-navmenu="Sesiones-Medio"}
====================================================


### Peoplemedia
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='peoplemedia') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Teads {data-navmenu="Sesiones-Medio"}
====================================================


### Teads
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='teads') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```



Youtube {data-navmenu="Sesiones-Medio"}
====================================================


### Youtube
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='youtube') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = ses)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("Sesiones, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```




Facebook {data-navmenu="CR-Medio"}
====================================================


### Facebook
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='facebook') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Google {data-navmenu="CR-Medio"}
====================================================


### Google
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='google') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Mediamath {data-navmenu="CR-Medio"}
====================================================


### Mediamath
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='mediamath') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Peoplemedia {data-navmenu="CR-Medio"}
====================================================


### Peoplemedia
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='peoplemedia') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```


Teads {data-navmenu="CR-Medio"}
====================================================


### Teads
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='teads') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```



Youtube {data-navmenu="CR-Medio"}
====================================================


### Youtube
  
```{r, echo=FALSE}
dat=df %>% group_by(Month,monthf,monthweek_compra,dia_purchase,
                    dia_semana_compra) %>%filter(Source=='youtube') %>%  summarise(ses=sum(Sesiones),add=sum(Add_to_cart),n=(add/ses)*100) %>%
                      arrange(dia_purchase)


# Now for the plot
P<- ggplot(na.omit(dat), aes(monthweek_compra, (reorder(dia_semana_compra,dia_purchase)), fill = n)) + 
  geom_tile(colour = "white")+ facet_grid(~ reorder(monthf,Month))+ scale_fill_gradient2(low = "white",high = "blue") +
  ggtitle("CR, Mar-Jun 2019") +  xlab("\n\nWeek of the month")+  ylab("\n\nWeekday") 

ggplotly(P)

```




